Hierarchical Learning for Chagas Detection from ECG under Expert-Label Scarcity

### 2025-04-15 contents/unofficial_abstract.tex
finish unofficial phase abstract

% The title is set in 14-point Helvetica bold
\title{To write}

@@

Aim: to write

Methods: to write

Results: to write

Conclusion: to write

>>>>

% The title is set in 14-point Helvetica bold
% \title{Hierarchical Learning with Clinical Expertise Integration for Chagas Detection from ECG under Data Scarcity Constraints}
\title{Hierarchical Learning for Chagas Detection from ECG under Expert-Label Scarcity}

@@

% Aim: This paper tackles automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), as the George B. Moody PhysioNet Challenge 2025 proposes.
Aim: This paper introduces a reliability-aware hierarchical learning framework for automated Chagas cardiomyopathy screening from electrocardiograms (ECGs), serving as the ``Revenger'' team's solution to the George B. Moody PhysioNet Challenge 2025.

Methods: ECGs were preprocessed through resampling to 400 Hz, 0.5-45 Hz Butterworth bandpass filtering, and z-score normalization to zero mean and unit variance. We implemented a convolutional neural network (CNN) based on the ResNet architecture with integrated squeeze-and-excitation (SE) modules for binary prediction (Chagas negative/positive). The public training data are highly imbalanced, with only approximately 2\% positive samples and an even larger scarcity (0.2\%) of expert-labeled samples, where the rest are patient self-reported. We employed a hierarchical upsampling and label smoothing scheme that prioritizes expert-validated samples over patient-reported ones. Expert-validated samples received a higher upsampling rate and a lower label smoothing factor (indicating higher reliability). Our model was optimized using asymmetric loss to further penalize false negatives, and with Adam optimizer and \texttt{OneCycle} learning rate scheduler for rapid convergence. A demographic feature-based stratified split was conducted to reserve 20\% of the data for model selection based on the challenge score: maximizing true positive rate while keeping positive predictions under 5\% prevalence.

Results: Our approach received a challenge score of 0.290 (Ranking: 76) on the hidden validation set. In our internal evaluation, the highest score was 0.456.

Conclusion: The proposed method establishes an effective foundation for automated Chagas screening through ECG analysis in resource-limited settings, yet presents clear opportunities for refinement to enhance detection performance and clinical applicability.
